Figures

### 2021-07-20 inst/manuscript/figures.Rmd
Fully revised manuscript (except abstract), SI, and figures.

g <- cowplot::plot_grid(p1, p2, nrow = 2, align = "hv", axis = "l",
                        labels = LETTERS[1:2], label_x = 0, 
                        label_y = c(0.97, 1),   
                        scale = c(1, 1), rel_heights = c(1, 0.7))
ggsave(pth("figures/figure4.png"), 
       width = 4, height = 6.5, units = "in", dpi = 300)

@@

### Figure 5: Active learning gain
```{r, eval=FALSE}
# iteration metrics
data("iteration_metrics")

@@

ggsave(pth("figures/figure5.png"), 
       width = 7, height = 4, units = "in", dpi = 300)
```

### Figure 6: The impact of training data error
```{r, eval=FALSE}
data("consensus_high_low")

@@

cols <- c("grey50", "grey60", "grey70", "grey80", "black")
sizes <- c(rep(1.5, 4), 2)
shapes <- c(3, 4, 8, 10, 16)
p <- ggplot(consensus_high_low_mu) + 
  geom_point(aes(x = Strategy, y = Score, color = AOI, size = AOI, 
                 shape = AOI)) + 
  ylim(0.4, 1) + xlab("Labelling strategy") + 
  scale_color_manual(values = cols) +
  scale_size_manual(values = sizes) + 
  scale_shape_manual(values = shapes) + 
  facet_wrap(~Metric) + 
  theme_linedraw() + 
  theme(legend.position = "bottom", 
        strip.background = element_rect(fill = "white"), 
        strip.text = element_text(colour = "black"))
ggsave(pth("figures/figure6.png"), height = 4, width = 6, dpi = 300)
```

@@

### Figure 7: Cropland maps
```{r, eval=FALSE}
# segment files
segment_files <- dir(here("external/data/results/segments/merged"),
                     pattern = "boundarymerge", full.names = TRUE)
iid <- as.numeric(gsub("[[:alpha:]]|_|\\.", "", basename(segment_files)))
segment_files <- tibble(file = segment_files, order = iid) %>% arrange(iid)
segment_files <- segment_files %>% filter(!grepl("aoi3_*.*merge.geojson", file))

@@

ggsave(filename = pth("figures/figure7.png"), 
       plot = inset_map, bg = "transparent", width = diff(maprange[1:2]), 
       height = diff(maprange[3:4]), units = "in", dpi = 300)

@@

### Figure S7: Label count and quality
```{r labelquality, eval=FALSE}
data("label_summary")

@@

# Q site accuracy
p1 <- ggplot(label_quality2) + 
  geom_boxplot(aes(x = reorder(ID, -score), y = score, fill = ID), 
               col = "grey50", varwidth = TRUE, show.legend = FALSE,
               outlier.size = 1) + 
  geom_point(aes(x = ID, y = Mean), shape = 4, size = 2) +
  scale_y_continuous(breaks = seq(0, 1, 0.1), limits = c(0, 1), 
                     expand = c(0, 0.01)) + 
  scale_fill_manual(values = rep("grey", length(unique(label_quality2$ID)))) + 
  xlab("ID") + ylab("Score") + 
  theme_linedraw() + 
  theme(axis.text = element_text(size = 11), 
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))

# N sites by type
yl <- c(0, ceiling(max(label_summary$nlabels$n) * 1.01))
p2 <- label_summary$nlabels %>% filter(!ID %in% toofewq$ID) %>% 
  group_by(ID, kml_type) %>% 
  ggplot() + 
  geom_bar(aes(x = reorder(ID, -n), y = n, fill = kml_type), 
           position = "dodge", stat = "identity") +
  xlab("ID") + ylab("N") + 
  labs(fill = "Map Type") + 
  scale_fill_manual(values = c("grey40", "grey70")) + 
  scale_y_continuous(breaks = seq(yl[1], yl[2], by = 200), 
                     expand = c(0, 0.01), limits = yl) + 
  theme_linedraw() + 
  theme(legend.position = c(0.7, 0.85), axis.text = element_text(size = 11), 
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))

cp_theme <- theme(axis.text = element_text(size = 11),  
                  legend.text = element_text(size = 11),
                  legend.title = element_text(size = 11),
                  axis.title = element_text(size = 12))
gp <- cowplot::plot_grid(p2 + cp_theme, p1 + cp_theme, nrow = 2, 
                         labels = LETTERS[1:2], label_x = 0.0) 
                         #rel_widths = c(0.65, 0.45))
ggsave(pth("figures/si_training_qual_n.png"), width = 4, 
       height = 8, units = "in", dpi = 300, bg = "transparent")
```

### Figures S8 and S9: Consensus label (Bayesian) risk

@@

### Figure S10: Random versus active sampling
```{r, eval=FALSE}
data("iteration_metrics")

### Figure S11: Training data error impact on probability images
```{r, eval = FALSE}
probpal <- viridis::viridis
cprob <- raster(here::here("external/prob/image_c294_r532.tif"))
hprob <- raster(here::here("external/prob/image_c294_r532_high.tif"))
lprob <- raster(here::here("external/prob/image_c294_r532_low.tif"))

@@

### Figures S12 and S13: Segmentation statistics (grid scale)

@@

### Figure S14: Average fields sizes

>>>>

g <- cowplot::plot_grid(p1, p2, nrow = 2, align = "hv", axis = "l",
                        labels = LETTERS[1:2], label_x = 0, 
                        label_y = c(0.97, 1),   
                        scale = c(1, 1), rel_heights = c(1, 0.7))
ggsave(pth("figures/figure3.png"), 
       width = 4, height = 6.5, units = "in", dpi = 300)

@@

### Figure 4: Active learning gain
```{r, eval=FALSE}
# iteration metrics
data("iteration_metrics")

@@

ggsave(pth("figures/figure4.png"), 
       width = 7, height = 4, units = "in", dpi = 300)
```

### Figure 5: The impact of training data error
```{r, eval=FALSE}
data("consensus_high_low")

@@

cols <- c("grey50", "grey60", "grey70", "grey80", "black")
sizes <- c(rep(1.5, 4), 2)
shapes <- c(3, 4, 8, 10, 16)
p <- ggplot(consensus_high_low_mu) + 
  geom_point(aes(x = Strategy, y = Score, color = AOI, size = AOI, 
                 shape = AOI)) + 
  ylim(0.4, 1) + xlab("Labelling strategy") + 
  scale_color_manual(values = cols) +
  scale_size_manual(values = sizes) + 
  scale_shape_manual(values = shapes) + 
  facet_wrap(~Metric) + 
  theme_linedraw() + 
  theme(legend.position = "bottom", 
        strip.background = element_rect(fill = "white"), 
        strip.text = element_text(colour = "black"))
ggsave(pth("figures/figure5.png"), height = 4, width = 6, dpi = 300)
```

@@

### Figure 6: Cropland maps
```{r, eval=FALSE}
# segment files
segment_files <- dir(here("external/data/results/segments/merged"),
                     pattern = "boundarymerge", full.names = TRUE)
iid <- as.numeric(gsub("[[:alpha:]]|_|\\.", "", basename(segment_files)))
segment_files <- tibble(file = segment_files, order = iid) %>% arrange(iid)
segment_files <- segment_files %>% filter(!grepl("aoi3_*.*merge.geojson", file))

@@

ggsave(filename = pth("figures/figure6.png"), 
       plot = inset_map, bg = "transparent", width = diff(maprange[1:2]), 
       height = diff(maprange[3:4]), units = "in", dpi = 300)

@@

### Figure S7: Assignment count
```{r assignmentcount, eval=FALSE}
data("label_summary")

@@

# N sites by type
yl <- c(0, ceiling(max(label_summary$nlabels$n) * 1.01))
p <- label_summary$nlabels %>% filter(!ID %in% toofewq$ID) %>% 
  group_by(ID, kml_type) %>% 
  ggplot() + 
  geom_bar(aes(x = reorder(ID, -n), y = n, fill = kml_type), 
           position = "dodge", stat = "identity") +
  xlab("ID") + ylab("N") + 
  labs(fill = "Label Type") + 
  scale_fill_manual(labels = c("Training/validation", "Accuracy assessment"),
                    values = c("grey40", "grey70")) + 
  scale_y_continuous(breaks = seq(yl[1], yl[2], by = 200), 
                     expand = c(0, 0.01), limits = yl) + 
  theme_linedraw() + 
  # theme(legend.position = c(0.7, 0.85), axis.text = element_text(size = 11),
  theme(axis.text = element_text(size = 11), 
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))

ggsave(pth("figures/si_training_n.png"), width = 5.5, 
       height = 4, units = "in", dpi = 300, bg = "transparent")
```

### Figure S8: Random versus active sampling
```{r, eval=FALSE}
data("iteration_metrics")

### Figure S9: Label quality
```{r labelquality, eval=FALSE}
# Plot data from Figure S7

# Q site accuracy
p <- ggplot(label_quality2) + 
  geom_boxplot(aes(x = reorder(ID, -score), y = score, fill = ID), 
               col = "grey50", varwidth = TRUE, show.legend = FALSE,
               outlier.size = 1) + 
  geom_point(aes(x = ID, y = Mean), shape = 4, size = 2) +
  scale_y_continuous(breaks = seq(0, 1, 0.1), limits = c(0, 1), 
                     expand = c(0, 0.01)) + 
  scale_fill_manual(values = rep("grey", length(unique(label_quality2$ID)))) + 
  xlab("ID") + ylab("Score") + 
  theme_linedraw() + 
  theme(axis.text = element_text(size = 11), 
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))

ggsave(pth("figures/si_label_quality.png"), width = 4, 
       height = 4, units = "in", dpi = 300, bg = "transparent")
```

### Figures S10 and S11: Consensus label (Bayesian) risk

@@

### Figure S12: Training data error impact on probability images
```{r, eval = FALSE}
probpal <- viridis::viridis
cprob <- raster(here::here("external/prob/image_c294_r532.tif"))
hprob <- raster(here::here("external/prob/image_c294_r532_high.tif"))
lprob <- raster(here::here("external/prob/image_c294_r532_low.tif"))

@@

### Figures S13 and S14: Segmentation statistics (grid scale)

@@

### Figure S15: Average fields sizes
